---
title: "Data Challenge for Data Science Intern Candidates"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Data

```{r load_data}
hospital_data <- read.csv('hospital_mortality.csv')
head(hospital_data)
```

Please include your code and results below.  Include comments and graphics where appropriate.  

## How many patients have 20 or more missing feature values?

```{r question_1}
## your code here
```

## What’s the difference in means of HR_min for patients that died vs survived (not counting patients with HR_min of 0)?

```{r question_2}
## your code here
```

## What is the median maximum heart rate for patients whose maximum temperature was 2 degrees Celsius higher than their minimum temperature?

```{r question_3}
## your code here
```

## Create a plot to analyze the relationship between median temperature, outcome (died vs. survived), and age.

```{r question_4a}
## your code here
```

## Create a plot to analyze the relationship between median temperature, outcome (died vs. survived), and gender.

```{r question_4b}
## your code here
```

## Build and summarize the results of a machine learning model that predicts whether a patient dies or survives in the hospital. (We do not expect a perfect or highest-accuracy solution; this is primarily an opportunity for you to show your machine learning project workflow and to document your thought process, approach to solving problems, and interpretation of results.)

```{r question_5}
## your code here
```
